Plug-and-Play Dual-Tree Algorithm Runtime Analysis

### 2015-12-28 bounds-files/imbalance.tex
JMLR style guide: "don't use utilize".

This sort of imbalance applies to all types of trees, not just $kd$-trees.  In
our situation, we are interested in a better understanding of this imbalance for
cover trees, and thus endeavor to introduce a more formal measure of imbalance
which is correlated with tree performance.  Numerous measures of tree
imbalance have already been established; one example is that proposed by
\citet{colless1982review}, and another is Sackin's index \citep{sackin1972good},
but we aim to capture a different measure of imbalance that utilizes the leveled
structure of the cover tree.

>>>>

This sort of imbalance applies to all types of trees, not just $kd$-trees.  In
our situation, we are interested in a better understanding of this imbalance for
cover trees, and thus endeavor to introduce a more formal measure of imbalance
which is correlated with tree performance.  Numerous measures of tree
imbalance have already been established; one example is that proposed by
\citet{colless1982review}, and another is Sackin's index \citep{sackin1972good},
but we aim to capture a different measure of imbalance that uses the leveled
structure of the cover tree.
